VSEARCH clustering

### 2020-10-28 exploratory/2020/sub4_vsearch.Rmd

dat <- bind_rows(optifit, opticlust) %>% 
  mutate(tool = "mothur") %>% 
  bind_rows(vsearch) %>% 
  mutate(mem_mb = max_rss,
         mem_gb = mem_mb / 1024,
         sec = s)
```

@@

```{r vsearch_mcc}
dat_filt %>% ggplot(aes(x = tool, y = mcc, color = dataset)) +
  geom_boxplot() +
  facet_wrap('method') +
  scale_color_manual(values = dataset_colors) +
  ylim(0, 1)
```

@@

```{r vsearch_runtime}
dat_filt %>% ggplot(aes(x = tool, y = sec, color = dataset)) +
  geom_boxplot() +
  facet_wrap('method') +
  scale_color_manual(values = dataset_colors)
dat_filt %>% ggplot(aes(x = tool, y = mem_gb, color = dataset)) +
  geom_boxplot() +
  facet_wrap('method') +
  scale_color_manual(values = dataset_colors)
```

@@

```{r vsearch_fraction}
dat_filt %>% filter(method == 'closed') %>% 
  ggplot(aes(x = tool, y = fraction_mapped, color = dataset)) +
  geom_boxplot() +
  scale_color_manual(values = dataset_colors) +
  ylim(0, 1)
```

>>>>

dat <- bind_rows(optifit, opticlust) %>% 
  mutate(tool = "mothur") %>% 
  bind_rows(vsearch) %>% 
  mutate(mem_mb = max_rss,
         mem_gb = mem_mb / 1024,
         sec = s) %>% 
  filter(ref %in% c('gg', NA))
```

@@

```{r vsearch_mcc}
mcc <- dat %>% ggplot(aes(x = method, y = mcc, color = tool)) +
  geom_boxplot() +
  facet_wrap('dataset', ncol = 1) +
  ylim(0, 1) + 
  labs(x = '')
mcc
```

@@

```{r vsearch_runtime}
sec <- dat %>% ggplot(aes(x = method, y = sec, color = tool)) +
  geom_boxplot() +
  facet_wrap('dataset', scales = 'free', ncol = 1)  +
  labs(x = '')
sec
mem <- dat %>% ggplot(aes(x = method, y = mem_gb, color = tool)) +
  geom_boxplot() +
  facet_wrap('dataset', scales = 'free', ncol = 1)  +
  labs(x = '')
mem
```

@@

```{r vsearch_fraction}
dat %>% filter(method == 'closed') %>% 
  ggplot(aes(x = method, y = fraction_mapped, color = tool)) +
  geom_boxplot() +
  facet_wrap('dataset') +
  ylim(0, 1) +
  labs(caption = 'Sequences were aligned to the greengenes database.')
```

## All metrics summarized on one plot

```{r vsearch_summary}
dat %>% pivot_longer(c(mcc, sec, mem_gb), names_to = 'metric') %>% 
  ggplot(aes(x = method, y = value, color = tool)) +
  geom_boxplot() +
  facet_wrap(dataset ~ metric, scales = 'free', ncol = 3, nrow = 4) + 
  labs(caption = "For reference clustering, the soil dataset was fit to the greengenes db.") +
  theme(axis.title = element_blank())
```

```{r vsearch_cowplot}
legend <- get_legend(mcc)
pgrid <- plot_grid(mcc + theme(legend.position = 'none'), 
          sec + theme(legend.position = 'none'), 
          mem + theme(legend.position = 'none'), 
          align = 'h', nrow = 1)
plot_grid(pgrid, legend, rel_widths = c(3, .4))
```
